Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2023-11-21 manuscript/manuscript.Rmd
Updated weights.

\midrule
non-robust               & ---  & ---       & ---  & ---  & ---       & ---  & 773 \\
$p^{*}$ (step)           & 0.80 & $(0, 1]$  & 0.84 & ---  & ---       & ---  & 598 \\
$p^{*}$ (triangle)       & 0.80 & $(0, 1]$  & 0.79 & 0.95 & $(0, 1]$  & 0.98 & 594 \\
$p^{*}$ (tapered cosine) & 0.80 & $(0, 1]$  & 0.77 & 0.95 & $(0, 1]$  & 1.00 & 580 \\
$z$ (step)               & 1.28 & $(0, 10]$ & 1.21 & ---  & ---       & ---  & 1214 \\
$z$ (triangle)           & 1.28 & $(0, 10]$ & 1.05 & 1.96 & $(0, 10]$ & 4.47 & 1052 \\
$z$ (tapered cosine)     & 1.28 & $(0, 10]$ & 1.09 & 1.96 & $(0, 10]$ & 5.30 & 1086 \\
$r$ (step)               & 0.50 & $(0, 10]$ & 1.36 & ---  & ---       & ---  & 1483 \\
$r$ (triangle)           & 0.50 & $(0, 10]$ & 1.43 & 1.00 & $(0, 10]$ & 1.45 & 1498 \\
$r$ (tapered cosine)     & 0.50 & $(0, 10]$ & 1.20 & 1.00 & $(0, 10]$ & 1.48 & 1467 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

```{=latex}
\begin{table}
\begin{center}
\caption{Optimal weighting parameters and corresponding loss for \textbf{shift-sensitive Yeo-Johnson} power transformations. $p^{*}$ indicates use of the empirical distribution of feature values, $z$ the z-score of the transformed feature values, and $r$ the residual error between the z-score of transformed feature values and the expected z-score according to the normal distribution. The \textit{initial} column shows the starting parameter value for the optimisation process, with the corresponding boundary values in the \textit{limits} column. The {optimal} column shows the optimal parameter values. The \textit{loss} column shows the loss achieved by each method, under optimised parameters. Lower loss indicates better robustness against outliers.}
\label{tab:optimal-weighting-parameters-yeo-johnson}
\begin{tabular}{l r r r r r r r}

@@

\midrule
non-robust               & ---  & ---       & ---  & ---  & ---       & ---  & 305 \\
$p^{*}$ (step)           & 0.80 & $(0, 1]$  & 0.87 & ---  & ---       & ---  & 136 \\
$p^{*}$ (triangle)       & 0.80 & $(0, 1]$  & 0.83 & 0.95 & $(0, 1]$  & 0.88 & 133 \\
$p^{*}$ (tapered cosine) & 0.80 & $(0, 1]$  & 0.81 & 0.95 & $(0, 1]$  & 0.88 & 133 \\
$z$ (step)               & 1.28 & $(0, 10]$ & 1.07 & ---  & ---       & ---  & 333 \\
$z$ (triangle)           & 1.28 & $(0, 10]$ & 1.00 & 1.96 & $(0, 10]$ & 4.57 & 227 \\
$z$ (tapered cosine)     & 1.28 & $(0, 10]$ & 0.55 & 1.96 & $(0, 10]$ & 5.16 & 236 \\
$r$ (step)               & 0.50 & $(0, 10]$ & 1.57 & ---  & ---       & ---  & 631 \\
$r$ (triangle)           & 0.50 & $(0, 10]$ & 1.28 & 1.00 & $(0, 10]$ & 1.81 & 562 \\
$r$ (tapered cosine)     & 0.50 & $(0, 10]$ & 1.32 & 1.00 & $(0, 10]$ & 1.75 & 567 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

>>>>

\midrule
non-robust               & ---  & ---       & ---  & ---  & ---       & ---  & 771 \\
$p^{*}$ (step)           & 0.80 & $(0, 1]$  & 0.86 & ---  & ---       & ---  & 561 \\
$p^{*}$ (triangle)       & 0.80 & $(0, 1]$  & 0.83 & 0.95 & $(0, 1]$  & 0.92 & 564 \\
$p^{*}$ (tapered cosine) & 0.80 & $(0, 1]$  & 0.76 & 0.95 & $(0, 1]$  & 0.95 & 560 \\
$z$ (step)               & 1.28 & $(0, 10]$ & 1.12 & ---  & ---       & ---  & 1153 \\
$z$ (triangle)           & 1.28 & $(0, 10]$ & 0.38 & 1.96 & $(0, 10]$ & 4.48 & 1178 \\
$z$ (tapered cosine)     & 1.28 & $(0, 10]$ & 1.21 & 1.96 & $(0, 10]$ & 4.92 & 1135 \\
$r$ (step)               & 0.50 & $(0, 10]$ & 2.18 & ---  & ---       & ---  & 1839 \\
$r$ (triangle)           & 0.50 & $(0, 10]$ & 1.29 & 1.00 & $(0, 10]$ & 1.47 & 1764 \\
$r$ (tapered cosine)     & 0.50 & $(0, 10]$ & 1.38 & 1.00 & $(0, 10]$ & 1.41 & 1583 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

```{=latex}
\begin{table}
\begin{center}
\caption{Optimal weighting parameters and corresponding loss for \textbf{invariant Yeo-Johnson} power transformations. $p^{*}$ indicates use of the empirical distribution of feature values, $z$ the z-score of the transformed feature values, and $r$ the residual error between the z-score of transformed feature values and the expected z-score according to the normal distribution. The \textit{initial} column shows the starting parameter value for the optimisation process, with the corresponding boundary values in the \textit{limits} column. The {optimal} column shows the optimal parameter values. The \textit{loss} column shows the loss achieved by each method, under optimised parameters. Lower loss indicates better robustness against outliers.}
\label{tab:optimal-weighting-parameters-yeo-johnson}
\begin{tabular}{l r r r r r r r}

@@

\midrule
non-robust               & ---  & ---       & ---  & ---  & ---       & ---  & 364 \\
$p^{*}$ (step)           & 0.80 & $(0, 1]$  & 0.95 & ---  & ---       & ---  & 224 \\
$p^{*}$ (triangle)       & 0.80 & $(0, 1]$  & 0.88 & 0.95 & $(0, 1]$  & 0.97 & 212 \\
$p^{*}$ (tapered cosine) & 0.80 & $(0, 1]$  & 0.94 & 0.95 & $(0, 1]$  & 0.95 & 218 \\
$z$ (step)               & 1.28 & $(0, 10]$ & 1.09 & ---  & ---       & ---  & 392 \\
$z$ (triangle)           & 1.28 & $(0, 10]$ & 0.24 & 1.96 & $(0, 10]$ & 4.62 & 396 \\
$z$ (tapered cosine)     & 1.28 & $(0, 10]$ & 0.15 & 1.96 & $(0, 10]$ & 6.05 & 413 \\
$r$ (step)               & 0.50 & $(0, 10]$ & 1.63 & ---  & ---       & ---  & 746 \\
$r$ (triangle)           & 0.50 & $(0, 10]$ & 1.50 & 1.00 & $(0, 10]$ & 1.79 & 731 \\
$r$ (tapered cosine)     & 0.50 & $(0, 10]$ & 1.51 & 1.00 & $(0, 10]$ & 1.57 & 612 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```
